\begin{thebibliography}{9}
    \bibitem{AASA2024}
        AASA (2024). \textit{Top 10 Problems on the Job}. The School Superintendents Association.
    \bibitem{Dataintelo2024} 
        Dataintelo (2024). \textit{Science Lab Equipment For Education Market Research Report 2033}.
    \bibitem{GFOA2024} 
        GFOA (2024). \textit{The End of ESSER: The Fiscal Cliff for School Districts}. Government Finance Officers Association.
    \bibitem{Market2024} 
        \textit{STEM Education In K--12 Market Size, Share}.
    \bibitem{MarketIntelo2024} 
        MarketIntelo (2024). \textit{Virtual Labs Market Research Report 2033}.
    \bibitem{NFPA2024} 
        NFPA (2024). \textit{Lithium-Ion Battery Safety}. National Fire Protection Association.
    \bibitem{PASCO2025} 
        PASCO Scientific (2025). \textit{Mechanics Starter Kit (ME-5300)}.
    \bibitem{ToolkitTechnologies2024} 
        Toolkit Technologies (2024). \textit{Horizon Renewable Energy Science Kit 2.0}.
    \bibitem{Hunt2023}
        B.~Zakeri \textit{et al.}, “Underground Gravity Energy Storage: A Solution for Long-Term Energy Storage,” IIASA News Release, Jan. 2023.
    \bibitem{RTBC2024} 
        “Abandoned Coal Mines are Becoming the Batteries of the Future,” \textit{Reasons to be Cheerful}, 2024.
    \bibitem{TheWeek} 
        Justin Klawans, \emph{Abandoned mines pose hidden safety and environmental risks}, The Week (12 Dec 2024). Available at: \url{https://theweek.com/science/abandoned-mine-safety-risks}.
    \bibitem{Rekioua2023}
        Rekioua, D. (2023). Energy Storage Systems for Photovoltaic and Wind Systems: A Review. Energies, 16(9), 3893. https://doi.org/10.3390/en16093893
    \bibitem{EnergyVault}
        Energy Vault® - enabling a renewable worldTM through energy storage. (n.d.). https://www.energyvault.com/
    \bibitem{llcBT} 
        Llc, B. T. (2023, October 12). The Pros and Cons of lithium ion batteries: A deep dive. Bioenno Power. https://www.bioennopower.com/blogs/news/the-pros-and-cons-of-lithium-ion-batteries-a-deep-dive#:~:text=In%20conclusion%2C%20lithium%2Dion%20batteries,environmental%20impact%2C%20and%20temperature%20sensitivity.
\end{thebibliography}