\section*{Microsoft Copilot Responds}

    \subsection*{Step A — Core abilities of gravity-based energy storage (Worksheet 1 input)}
    
        Brief characterization (independent of any single product):

        \begin{itemize}[leftmargin=*]
          \item \textbf{Long-duration, mechanical energy storage} (hours to days), high cycle life and long operational lifetime \cite{mdpi}.
          \item \textbf{Low dependency on scarce or chemical materials} (steel, concrete, mechanical masses), potentially reducing supply-chain risk compared to Li-ion \cite{energystoragenews}.
          \item \textbf{Modular architectures} (tower, shaft, slope, rail, block-based) adaptable to site constraints \cite{epo}.
          \item \textbf{Low environmental hazard and maintenance}, no toxic electrolytes, long expected lifetimes \cite{energystoragenews}.
          \item \textbf{Strong fit for stationary, heavy-mass, high-throughput applications}, scaling with mass and height \cite{gmi}.
        \end{itemize}

        \subsection*{Step B — Worksheet 1: Market opportunities}
            \small
            \begin{longtable}{>{\raggedright}p{1cm} p{4.2cm} p{4cm} p{4.5cm} p{3.5cm}}
                \toprule
                \# & Opportunity & Primary market needs & How GBES meets the need & Evidence \\
                \midrule
                1 &
                Utility / grid-scale long-duration storage &
                Renewable firming, capacity, long life &
                Multi-hour to multi-day discharge, long lifetime, alternative to batteries and pumped hydro &
                \cite{gmi} \\
                
                2 &
                Co-located storage with wind/solar &
                Curtailment reduction, merchant value &
                Stores surplus generation; modular siting with plants &
                \cite{dataintelo} \\
                
                3 &
                Data centers and hyperscalers &
                High reliability, sustainability &
                Long-life mechanical UPS and long-duration backup &
                \cite{zincfive} \\
                
                4 &
                Mining and heavy industry &
                Remote, dispatchable power, decarbonization &
                Durable storage paired with renewables &
                \cite{komatsu} \\
                
                5 &
                EV fast-charging hubs &
                Peak shaving, grid constraints &
                Delivers high sustained power; defers grid upgrades &
                \cite{fortune} \\
                
                6 &
                Remote/off-grid communities and telecom &
                Reliable long-duration power &
                Low-maintenance storage paired with renewables &
                \cite{fortune} \\
                
                7 &
                Underground mine-shaft retrofits &
                Reuse existing shafts, lower civil cost &
                High energy density via vertical infrastructure &
                \cite{patentguru} \\
                
                8 &
                Building-integrated / urban skyscrapers &
                Local resilience, peak shaving &
                Shaft or tower-based storage at building scale &
                \cite{epo} \\
                
                9 &
                Industrial process-heat coupling &
                Industrial decarbonization &
                Load shifting for heat pumps and electric boilers &
                \cite{ldes} \\
                \bottomrule
                \end{longtable}
                \normalsize
                
                \section*{Step C — Worksheet 2: Opportunity evaluation}
                
                \small
                \begin{longtable}{>{\raggedright}p{1cm} p{4.8cm} p{3cm} p{3cm} p{4.5cm}}
                \toprule
                \# & Opportunity & Potential & Challenge & Rationale \\
                \midrule
                1 &
                Utility / grid-scale LDES &
                SUPER-HIGH &
                MID &
                Massive LDES demand; long procurement cycles and capex \cite{gmi} \\
                
                2 &
                Co-located renewables &
                HIGH &
                MID &
                Strong developer demand; moderate integration complexity \cite{dataintelo} \\
                
                3 &
                Data centers &
                HIGH &
                HIGH &
                Premium buyers but extreme reliability and incumbents \cite{zincfive} \\
                
                4 &
                Mining and heavy industry &
                HIGH &
                MID &
                Strong budgets; ruggedization and financing challenges \cite{komatsu} \\
                
                5 &
                EV charging hubs &
                MID &
                HIGH &
                Grid deferral value; strong BESS competition \cite{fortune} \\
                
                6 &
                Remote/off-grid and telecom &
                MID &
                LOW--MID &
                Smaller market but fast pilots and strong value proposition \cite{fortune} \\
                
                7 &
                Underground shaft retrofits &
                MID &
                HIGH &
                Capex synergies but regulatory and engineering complexity \cite{patentguru} \\
                
                8 &
                Building-integrated storage &
                LOW--MID &
                HIGH &
                Urban constraints and permitting risks \cite{epo} \\
                
                9 &
                Industrial process heat &
                MID &
                MID--HIGH &
                Decarbonization potential; system integration complexity \cite{ldes} \\
                \bottomrule
            \end{longtable}
            \normalsize

    \subsection*{Step D — Practical prioritization}
    
        \subsubsection*{Primary opportunities}
            \begin{itemize}
              \item Utility-scale long-duration storage \cite{gmi}.
              \item Co-location with large renewables \cite{dataintelo}.
            \end{itemize}
        
        \subsubsection*{Secondary opportunities}
            \begin{itemize}
              \item Mining and heavy industry \cite{komatsu}.
              \item Remote/off-grid communities and telecom \cite{mdpimicrogrids}.
            \end{itemize}
            
        \subsubsection*{Options to keep open}
            \begin{itemize}
              \item Data centers \cite{datacenterdynamics}.
              \item Underground shaft and building-integrated systems \cite{patentguru}.
            \end{itemize}

\subsection*{Gym User Interview Insights}

We conducted an initial gym–user interview and compared the responses to general observations about gym behaviour. Several insights were repeatedly confirmed:

\begin{enumerate}
  \item Users struggle to see progress during workouts without tracking apps.
  \item Many people find gym routines repetitive; anything that adds novelty helps motivation.
  \item Gym loyalty is low—people switch gyms for better equipment or experience.
  \item Sustainability matters, but only if it enhances the workout experience.
  \item The gravity system idea was received positively and described as “cool” or “interesting,” but users were realistic about the low energy output.
\end{enumerate}

Sample interview quotes include:
\begin{itemize}
  \item ``Most machines don't give you a real sense of progress. You just hope you're improving.''
  \item ``I get bored easily. Anything interactive or visual would keep me engaged longer.''
  \item ``If a gym had something unique like this, I'd try it for sure.''
\end{itemize}

\subsection*{GBES Lab Kit Interview Insights}

\textbf{Interviewee:} Mechanical Engineering Student (TU/e) \\
\textbf{Date:} 09/12/2025 \\
\textbf{Key Findings:} The interview provided strong validation for the visualization and curriculum aspects of the GBES Lab Kit, while offering a nuanced perspective on safety.

\paragraph{Validation of the "Invisible Energy" Problem} 
The student explicitly confirmed that current software-heavy labs fail to make abstract concepts intuitive. He described working with an adiabatic (compressed air) storage system where the energy storage was invisible, relying entirely on sensors and laptops. He stated that ``the data itself, without any context on a computer, is just harder to interpret,'' whereas ``manipulating something physically... allows you to comprehend things better, more naturally.'' This directly validates the core value proposition of the GBES kit: replacing invisible chemical storage with visible, mechanical potential energy that students can "grasp".

\paragraph{The Need for "Safe" Mechanics} 
While the student noted that his specific science lab used low-pressure models requiring no protective equipment, he revealed that his broader  experience has been influenced by safety risks from lab tools. He recounted a ``safety scare'' where a hacksaw blade ``quite literally snapped'' and a grinder slipped, noting it ``could have easily gotten to my fingers''. This highlights a gap for the GBES kit: it offers the physical, mechanical engagement students crave (``building/manipulating things'') without the high risks of the fabrication workshop.


        
    %\subsection*{References}
        \begin{thebibliography}{99}
            \bibitem{mdpi} MDPI, \textit{A Review of Gravity Energy Storage} \href{https://www.mdpi.com/1996-1073/18/7/1812}.
            \bibitem{energystoragenews} Energy-Storage.News, Patents for gravity energy storage.
            \bibitem{epo} European Patent Office, Gravity energy storage systems.
            \bibitem{gmi} Global Market Insights, Gravity-Based Energy Storage Market.
            \bibitem{dataintelo} DataIntelo, Gravity-Based Energy Storage Market Report.
            \bibitem{zincfive} ZincFive, Data Center Energy Storage Industry Insights.
            \bibitem{komatsu} Komatsu, \textit{The Electric Mine 2025}.
            \bibitem{fortune} Fortune Business Insights, Long-Duration Energy Storage Market.
            \bibitem{patentguru} PatentGuru, Gravitricity Ltd patents.
            \bibitem{ldes} Long Duration Energy Storage Council, Industrial Decarbonization.
            \bibitem{mdpimicrogrids} MDPI, Microgrids and Energy Storage Systems.
            \bibitem{datacenterdynamics} Data Center Dynamics, Google LDES partnership.
        \end{thebibliography}
